---
format: 
  html:
    self-contained: true
params:
  type: "gene"
  subtype: "gene"
  content: "ROCK1"
  private: "true"
title: "`r params$content` Report"
---

{{< include _setup.qmd >}}

### from `r dplyr::if_else(params$private == "true", paste0("datadrivenhypothesis.com"), paste0("datadrivenhypothesis.org"))`  
`r lubridate::stamp("Report generated December 31, 1979")(now())`  
  
## Project Summary  

Data-driven hypothesis is a resource for identifying novel functions for human genes developed by the [Hirschey Lab](www.hirscheylab.org). This project leverages several high-quality publicly available datasets, including release `r release` of the [Dependency Map](www.depmap.org) from the [Broad Institute](www.broadinstitute.org).  
  
## Gene Summary  
{{< include _gene-summary.qmd >}}  
{{< pagebreak >}}  
  
### Ideogram
{{< include _gene-ideogram.qmd >}}  
{{< pagebreak >}}  

```{r}
unlockBinding("params", env = .GlobalEnv)
params$content <- 'ROCK1'
```

## Gene Summary  
{{< include _gene-summary.qmd >}}  
{{< pagebreak >}}  

```{r}
params$content
```

  